File-based localization of numerical perturbations in data analysis pipelines

### 2020-05-02 paper.tex
Minor fixes

In neuroimaging, our primary application field, data analyses often consist
of hundreds of computational processes -- often coming from multiple
toolboxes -- that are aggregated to perform a specific function. For
instance, the fMRIprep pipeline~\cite{esteban2019fmriprep} assembles software blocks
from FSL~\cite{jenkinson2012fsl}, AFNI~\cite{cox2012afni}, FreeSurfer~\cite{fischl2012freesurfer} and ANTs~\cite{avants2009advanced} to provide a state-of-the art
functional MRI processing tool with minimal user input. Another example are the pipelines of the Human
Connectome Project~\cite{glasser2013} that combine tools from FSL and FreeSurfer to pre-process
structural, functional and diffusion data from their
uniquely high-fidelity open dataset. In both cases, pipelines leverage toolboxes that are
widely trusted in the community, yet, at the same time substantial variations in results
have been observed in these toolboxes resulting from minor data
or infrastructure perturbations~\cite{Gronenschild2012, Glatard2015, Lewis2017-ll}, suggesting that further investigation of their
numerical conditioning is required. For such complex pipelines, a
lightweight solution has to be found to perform such evaluations with
limited code instrumentation.

@@

We warmly thank Compute Canada (\url{http://www.computecanada.ca}) and Calcul
Qu\'ebec (\url{http://www.calculquebec.ca}) for providing the infrastructure used in our experiments.
Data and pipelines were provided by the Human Connectome Project, WU-Minn 
Consortium (Principal Investigators: David Van Essen and Kamil Ugurbil; 
1U54MH091657) funded by the 16 NIH Institutes and Centers that support 
the NIH Blueprint for Neuroscience Research; and by the McDonnell 
Center for Systems Neuroscience at Washington University.
\tristan{check ethics}

>>>>

In neuroimaging, our primary application field, data analyses often consist
of hundreds of computational processes -- often coming from multiple
toolboxes -- that are aggregated to perform a specific function. For
instance, the fMRIprep pipeline~\cite{esteban2019fmriprep} assembles software blocks
from FSL~\cite{jenkinson2012fsl}, AFNI~\cite{cox2012afni}, FreeSurfer~\cite{fischl2012freesurfer} and ANTs~\cite{avants2009advanced} to provide a state-of-the art
functional MRI processing tool with minimal user input. Another example are the pipelines of the Human
Connectome Project~\cite{glasser2013} that combine tools from FSL and FreeSurfer to pre-process
structural, functional and diffusion data from their
uniquely high-fidelity open dataset. In both cases, pipelines leverage toolboxes that are
widely trusted in the community, yet, at the same time substantial variations in results
have been observed in these toolboxes resulting from minor data
or infrastructure perturbations~\cite{Gronenschild2012, Glatard2015, Lewis2017-ll, kennedy2019everything}, suggesting that further investigation of their
numerical conditioning is required. For such complex pipelines, a
lightweight solution has to be found to perform such evaluations with
limited code instrumentation.

@@

We warmly thank Compute Canada (\url{http://www.computecanada.ca}) and Calcul
Qu\'ebec (\url{http://www.calculquebec.ca}) for providing the infrastructure used in our experiments.
Data and pipelines were provided by the Human Connectome Project, WU-Minn 
Consortium (Principal Investigators: David Van Essen and Kamil Ugurbil; 
1U54MH091657) funded by the 16 NIH Institutes and Centers that support 
the NIH Blueprint for Neuroscience Research; and by the McDonnell 
Center for Systems Neuroscience at Washington University.
%\tristan{check ethics}
